Modal Abstractions for Virtualizing Memory Addresses

### 2023-02-20 soundness.tex
+

\subsection{The Soundness Statement}
\label{def:soundness:statement}
The operational semantics of our simple lang just executes the instruction of our x86-64 model. Therefore, our soundness argument is to show that any execution composed of actions in our machine model (some of which are shown in Figure \sref{sec:semantics}) does not end-up in a invalid state.guarantees that  (\sref{sec:valid}). A~program that attempts to ... stuck~(\sref{sec:instrsemantics}).
\begin{theorem}[Soundness of the Logic]
  \label{th:adequacy}
  Assuming that $\triple{\textsf{valid\_init}}\instr\iTrue$ holds,
 The execution of the instruction~$\instrs$, beginning in an initial state, cannot result in a configuration where a thread is stuck.
\end{theorem}
which states that if the program~$\instr$, with the given \textsf{valid\_init} asserting a valid state initialization, satisfies a semantic Hoare
triple, then this program cannot crash: by a direct consequence of Iris's adequacy theorem~\cite[\S6.4]{iris}.

Moreover we need to show the validity of each rules in Figures \fref{fig:reasoning} and \fref{fig:laws}.
\begin{theorem}[Validity of the Reasoning Rules]
\label{th:validity}
  Each of the rules in Figures~\ref{fig:laws}
  and~\ref{fig:reasoning} is valid.
\end{theorem}
Due to the space limits in this paper, we do not mention each proof for these rules explicitly (which are already mechanized in Coq),
but the definitions and constructions used requires explanation.

>>>>

\subsection{The Soundness Statement}
\label{def:soundness:statement}
The operational semantics of our simple lang just executes sequences of instructions in our x86-64 model. Therefore, our soundness argument is to show that any execution composed of instructions in our machine model (some of which are shown in Figure \sref{sec:semantics}) does not end-up in a invalid state. In other words, a~program that attempts to ... stuck~(\sref{sec:instrsemantics}).
\begin{theorem}[Soundness of the Logic]
  \label{th:adequacy}
 Together with the assumptions on the initial state hold,
 the execution of the instruction~$\instrs$, beginning with this initial state, cannot result in a configuration where the execution is stuck.
\end{theorem}
which states that if the program~$\instr$, with the given \textsf{valid\_init} asserting a valid state initialization, satisfies a semantic Hoare
triple, then this program cannot crash: by a direct consequence of Iris's adequacy theorem~\cite[\S6.4]{iris}.
\todo{ismail, give the real adeq. theorem here}
Moreover we need to show the validity of each rules in Figures \fref{fig:reasoning} and \fref{fig:laws}.
\begin{theorem}[Validity of the Reasoning Rules]
\label{th:validity}
  Each of the rules in Figures~\ref{fig:laws}
  and~\ref{fig:reasoning} is valid.
\end{theorem}
Due to the space limits in this paper, we do not mention each proof for these rules explicitly (which are already mechanized in Coq),
but the definitions and constructions used requires explanation.
